Considering scale in multilayer animal social networks

### 2020-06-20 paper/manuscript.Rmd

---
title: Considering scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
   # bookdown::github_document2: default
   bookdown::word_document2:
     reference_docx: template.docx
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    # warning = FALSE,
    # message = FALSE,
    eval = TRUE,
    out.width = '\\linewidth'
)

@@

library(data.table)
DT <- readRDS('../data/derived-data/01-sub-fogo-caribou.Rds')
nobs <- readRDS('../data/derived-data/05-number-of-observations.Rds')
timedefs <- fread('../data/supp-data/timecut-defs.csv')
```

>>>>

---
title: Considering scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
   # bookdown::github_document2: default
   bookdown::word_document2:
     reference_docx: template.docx
knit: (function(inputFile, encoding) {
  rmarkdown::render(input = inputFile, encoding = encoding, output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    eval = TRUE,
    out.width = '\\linewidth'
)

library(data.table)

@@

DT <- readRDS('../data/derived-data/01-sub-fogo-caribou.Rds')
nobs <- readRDS('../data/derived-data/05-number-of-observations.Rds')
timedefs <- fread('../data/supp-data/timecut-defs.csv')
```
